The effect of symbols in government communications on citizens' trust, and its interaction with substantive information

### 2018-06-14 paper2_information and symbols.Rmd
Add files via upload

filter_IP = N_0-(SVIVA2_00 %>%
  distinct(IP,.keep_all=TRUE) %>% nrow())
filter_age = N_0-(SVIVA2_00 %>%
  filter(!(AGE%in% 1:17))%>% nrow())
filter_IMC = N_0-(SVIVA2_00 %>%
  filter(IMC==1)%>% nrow())
filter_time = N_0-(SVIVA2_00 %>%
  filter(TIMER_total>=3,TIMER_total<=30) %>% nrow())

N_1_haifa = filter(SVIVA2_01,AREA==1) %>% nrow()
N_1_center = filter(SVIVA2_01,AREA==0) %>% nrow()

@@

To empirically test these theoretical expectations, I conducted a large randomized survey experiment among circa `r SVIVA2_01%>%nrow() %>% round(-1)` Israeli citizens. The experiment focuses on the empirical case of the Israeli Environment Protection Ministry. I explore citizens' responses to public communications about two policy plans of the Ministry, and specifically the extent to which their trust in these policies are affected by the substantive information of the communications (logically persuasive vs. unpersuasive policy plans) and by symbolic elements in them (real symbols vs. fake symbols and no symbols conditions).

@@

The survey experiment was conducted online through Qualtrics Survey Software. To subjects, adult Israeli citizens, were recruited via an Israeli internet research panel company - *iPanel*. The online survey link was sent by iPanel, between 28.1-1.2.2018 to 5,077 people. A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).[^footnote_responserate] Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`). These filters are not significantly associated with the experimental conditions. Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects (Mean age = `r SVIVA2_01%>%summarise(mean(AGE,na.rm=T))%>%max()%>%round(1)`, `r SVIVA2_01%>%summarise(mean(GENDER,na.rm=T)*100)%>%max()%>%round(1)`% women).[^footnote_sample_areas] Because each subjects evaluated two different policy plans, my dataset has a multilevel structure of `r SVIVA2_01_comb %>% nrow()` observations nested within these `r N_1` subjects.

@@

```{r, echo=FALSE, warning=FALSE, message=F}
alpha_air_trust = psych::alpha(select(SVIVA2_01, TRUST_air_q1,
                               TRUST_air_q2,
                               TRUST_air_q3,
                               TRUST_air_q4,
                               TRUST_air_q5,
                               TRUST_air_q6))[["total"]][["raw_alpha"]] %>% round(2)

alpha_waste_trust = psych::alpha(select(SVIVA2_01, TRUST_waste_q1,
                               TRUST_waste_q2,
                               TRUST_waste_q3,
                               TRUST_waste_q4,
                               TRUST_waste_q5,
                               TRUST_waste_q6))[["total"]][["raw_alpha"]] %>% round(2)

alpha_trust_comb = ((alpha_air_trust+alpha_waste_trust)/2) %>% round(2)

cor_elaboration_air = cor.test(SVIVA2_01$MEMORY_air_score,SVIVA2_01$ELABORATION_air_time_log,method="spearman")$estimate %>% mean() %>% round(2)

cor_elaboration_waste = cor.test(SVIVA2_01$MEMORY_waste_score,SVIVA2_01$ELABORATION_waste_time_log,method="spearman")$estimate %>% mean() %>% round(2)

@@

To assess the levels of thinking or elaboration on the policy plans, I used two distinct measures: First, I counted the number of seconds participants spent on scanning each of the policy plans (hereafter – reaction time), log transformed to reduce skewness (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(ELABORATION_time_log))%>%max()%>%round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(ELABORATION_time_log))%>%max()%>%round(2)`). Second, I used a memory test, asking participants whether a list of four items were included in the policy plan, of which two were/were not included (participants could also select "I don't know"). The memory score is calculated as the number of correct items selected by the participant minus the number of incorrect items, with a minimum score of zero. Accordingly, participants could receive the scores of 0 (`r filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow())/N_1*100)%>%round(1)`%), 1 (`r filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow())/N_1*100)%>%round(1)`%) or 2 (`r filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow())/N_1*100)%>%round(1)`%).[^footnote_elaboration] These two measures are correlated with each other (Spearman rho = `r ((cor_elaboration_air+cor_elaboration_waste)/2) %>% round(2)`, which substantiates their validity.

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE}
x_realsymbol = filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(trust)) %>% max()
x_fakesymbol = filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(trust)) %>% max()
x_nosymbol = filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(trust)) %>% max()
sd_trust = SVIVA2_01_comb%>%summarise(sd(trust))%>%max()

x_realsymbol_delta = filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(WITHIN_DELTA)) %>% max()
x_fakesymbol_delta = filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(WITHIN_DELTA)) %>% max()
x_nosymbol_delta = filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(WITHIN_DELTA)) %>% max()
sd_trust_delta = SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()

@@

In Model 1.2, the effect of the symbols remains intact, and the effect of the weak policy condition is negative and significant (*Coef* = `r mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())-1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())+1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`]). In Model 1.3, the interaction between weak policy and real symbols is positive and significant, whereas the interaction with the fake symbols is insignificant. The interpretation of this model suggests that the real symbols had a greater effect on trust when the policy plan was weak (*Coef* = `r mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`] and `r mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`] Compared with the no symbols and fake symbols, respectively). When added to the strong policy plan, the effect of the real symbols is weaker, and significant only compared with the no symbols condition (*Coef* = `r mod_1.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1). Congruently, the symbols decreased the differences in trust between the strong and weak policies by `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())/(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())*100) %>% round(0)`%, compared with the no symbols group (from `r mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`] to `r mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`]). The interaction between symbols and information significantly contributes to the model fit (Chi2 = `r anova(mod_1.3,mod_1.2)%>%tidy()%>%filter(term=="mod_1.3")%>%select(statistic)%>%max()%>%round(2)`, *p*<.05). To facilitate the interpretation of this interaction, **Figure 6** provides a descriptive demonstration of the effects of the real symbols on trust in policy, under weak and strong information quality.

@@

The interaction between between symbols can be also tested *within-subjects*, by comparing the averaged delta across the different symbols conditions. Based on my second hypothesis, I expect that the averaged delta will be lower among subjects in the real symbols condition. This comparison is graphically displayed in **Figure 6**. The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1] %>% round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2] %>% round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1] %>% round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2] %>% round(2)`], *t*= `r t_delta_symbol_nosymbol[["statistic"]][["t"]]` and `r t_delta_symbol_fakesymbol[["statistic"]][["t"]]`, respectively). The differences between the two control groups are insignificant. These results further support my above finding that familiar symbols decrease subjects' inclination to differentiate between the strong and weak policy plans.

@@

Altogether, the above between- and within-subject analyses largely support my first two hypothesis. They suggest that familiar symbolic elements in communications increase citizens' trust in policies which are presented, and that the effect is greater the less logically persuasive is the information in the communications. Symbols attenuate the negative effect of weak or logically unpersuasive information in communications.[^footnote_robust_analyses_1]

[^footnote_robust_analyses_1]: In other statistical models, shown in the supplementary appendix, I tested additional specifications, including ##TBA##. In all these robust analyses, the effect of the real symbols condition on trust in policy remains positive and significant, and the interaction bewteen the real symbols and the weak information remains positive and signifcant [##TBA##].

@@

cor_memory_nosymbol = cor.test(as.numeric(filter(SVIVA2_01_comb,SYMBOL!=1)$SYMBOL),
                               filter(SVIVA2_01_comb,SYMBOL!=1)$MEMORY_score, 
                               method="spearman")$estimate %>% mean() %>% round(2)

cor_memory_fakesymbol = cor.test(as.numeric(filter(SVIVA2_01_comb,SYMBOL!=0)$SYMBOL),
                               filter(SVIVA2_01_comb,SYMBOL!=0)$MEMORY_score, 
                               method="spearman")$estimate %>% mean() %>% round(2)
```

In **Table 2**, I test the effects of the real symbols on the elaboration measures via regression analyses. I regressed each measure on the symbols manipulation (Models 2.1, 2.3), and than added the information manipulation (Models 2.2, 2.4). The first two models, which refer to reaction time, are multilevel models which are similar to the analyses in table 1. As for the memory score analyses, given that each subject was asked only about one policy (the second in order), I used an OLS regression instead.

@@

Next, I tested the moderated mediation hypothesis. To do so, I used the causal mediation analysis method via `mediate` R package, which was developed by Imai et al. [@imai_2010; @imai_2011], and was also recently also implemented in Public Administration research [@porumbescu_2018]. This method predicts the change in the outcome variable (here: trust in policy) given the causal change in the mediator that would be induced by the treatment (here: decreased elaboration inducted by the real symbols). Accordingly, it enables to decipher the proportion of the causal mediation effect from the total effect. Causal mediation analysis is based on counter-factual comparisons, as opposed to the traditional method of @baron_1986, which is based on linear structural equation modeling. It is advantaged in terms of its accuracy as well as its ability to identify causality. The results of the causal analysis tables are summarized in **Table 3**.

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE}
#RT
table_med_RT__nosymbol_INFORMTION_0 = 
summary(med_RT__nosymbol_INFORMTION_0) %>% 
extract_mediation_summary()

table_med_RT__fakesymbol_INFORMTION_0 = 
summary(med_RT__fakesymbol_INFORMTION_0) %>% 
extract_mediation_summary()

table_med_RT__nosymbol_INFORMTION_1 = 
summary(med_RT__nosymbol_INFORMTION_1) %>% 
extract_mediation_summary()

table_med_RT__fakesymbol_INFORMTION_1 = 
summary(med_RT__fakesymbol_INFORMTION_1) %>% 
extract_mediation_summary()

#memory
table_med_memory__nosymbol_INFORMTION_0 = 
summary(med_memory__nosymbol_INFORMTION_0) %>% 
extract_mediation_summary()

table_med_memory__fakesymbol_INFORMTION_0 = 
summary(med_memory__fakesymbol_INFORMTION_0) %>% 
extract_mediation_summary()

table_med_memory__nosymbol_INFORMTION_1 = 
summary(med_memory__nosymbol_INFORMTION_1) %>% 
extract_mediation_summary()

table_med_memory__fakesymbol_INFORMTION_1 = 
summary(med_memory__fakesymbol_INFORMTION_1) %>% 
extract_mediation_summary()
```

@@

*Mediator: Reaction time*
3.1: Weak policy
```{r, echo=FALSE,warning=FALSE,message=FALSE}
table_med_RT_INFORMTION_0 = 
  cbind.data.frame(table_med_RT__nosymbol_INFORMTION_0,
                   table_med_RT__fakesymbol_INFORMTION_0)
library(kableExtra)

>>>>

filter_IP = N_0-(SVIVA2_00 %>%
  distinct(IP,.keep_all=TRUE)%>%nrow())
filter_age = N_0-(SVIVA2_00 %>%
  filter(!(AGE%in% 1:17))%>% nrow())
filter_IMC = N_0-(SVIVA2_00 %>%
  filter(IMC==1)%>% nrow())
filter_time = N_0-(SVIVA2_00 %>%
  filter(TIMER_total>=3,TIMER_total<=30)%>%nrow())

N_1_haifa = filter(SVIVA2_01,AREA==1)%>%nrow()
N_1_center = filter(SVIVA2_01,AREA==0)%>%nrow()

@@

To empirically test these theoretical expectations, I conducted a large randomized survey experiment among circa `r SVIVA2_01%>%nrow()%>%round(-1)` Israeli citizens. The experiment focuses on the empirical case of the Israeli Environment Protection Ministry. I explore citizens' responses to public communications about two policy plans of the Ministry, and specifically the extent to which their trust in these policies are affected by the substantive information of the communications (logically persuasive vs. unpersuasive policy plans) and by symbolic elements in them (real symbols vs. fake symbols and no symbols conditions).

@@

The survey experiment was conducted online through Qualtrics Survey Software. To subjects, adult Israeli citizens, were recruited via an Israeli internet research panel company - *iPanel*. The online survey link was sent by iPanel, between 28.1-1.2.2018 to 5,077 people. A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).[^footnote_responserate] Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`). These filters are not significantly associated with the experimental conditions. Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects (Mean age = `r SVIVA2_01%>%summarise(mean(AGE,na.rm=T))%>%max()%>%round(1)`, `r SVIVA2_01%>%summarise(mean(GENDER,na.rm=T)*100)%>%max()%>%round(1)`% women).[^footnote_sample_areas] Because each subjects evaluated two different policy plans, my dataset has a multilevel structure of `r SVIVA2_01_comb%>%nrow()` observations nested within these `r N_1` subjects.

@@

```{r, echo=FALSE, warning=FALSE, message=F}
alpha_air_trust = psych::alpha(select(SVIVA2_01, TRUST_air_q1,
                               TRUST_air_q2,
                               TRUST_air_q3,
                               TRUST_air_q4,
                               TRUST_air_q5,
                               TRUST_air_q6))[["total"]][["raw_alpha"]]%>%round(2)

alpha_waste_trust = psych::alpha(select(SVIVA2_01, TRUST_waste_q1,
                               TRUST_waste_q2,
                               TRUST_waste_q3,
                               TRUST_waste_q4,
                               TRUST_waste_q5,
                               TRUST_waste_q6))[["total"]][["raw_alpha"]]%>%round(2)

alpha_trust_comb = ((alpha_air_trust+alpha_waste_trust)/2)%>%round(2)

cor_elaboration_air = cor.test(SVIVA2_01$MEMORY_air_score,SVIVA2_01$ELABORATION_air_time_log,method="spearman")$estimate%>%mean()%>%round(2)

cor_elaboration_waste = cor.test(SVIVA2_01$MEMORY_waste_score,SVIVA2_01$ELABORATION_waste_time_log,method="spearman")$estimate%>%mean()%>%round(2)

@@

To assess the levels of thinking or elaboration on the policy plans, I used two distinct measures: First, I counted the number of seconds participants spent on scanning each of the policy plans (hereafter – reaction time), log transformed to reduce skewness (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(ELABORATION_time_log))%>%max()%>%round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(ELABORATION_time_log))%>%max()%>%round(2)`). Second, I used a memory test, asking participants whether a list of four items were included in the policy plan, of which two were/were not included (participants could also select "I don't know"). The memory score is calculated as the number of correct items selected by the participant minus the number of incorrect items, with a minimum score of zero. Accordingly, participants could receive the scores of 0 (`r filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow())/N_1*100)%>%round(1)`%), 1 (`r filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow())/N_1*100)%>%round(1)`%) or 2 (`r filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow())/N_1*100)%>%round(1)`%).[^footnote_elaboration] These two measures are correlated with each other (Spearman rho = `r ((cor_elaboration_air+cor_elaboration_waste)/2)%>%round(2)`, which substantiates their validity.

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE}
x_realsymbol = filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(trust))%>%max()
x_fakesymbol = filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(trust))%>%max()
x_nosymbol = filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(trust))%>%max()
sd_trust = SVIVA2_01_comb%>%summarise(sd(trust))%>%max()

x_realsymbol_delta = filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(WITHIN_DELTA))%>%max()
x_fakesymbol_delta = filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(WITHIN_DELTA))%>%max()
x_nosymbol_delta = filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(WITHIN_DELTA))%>%max()
sd_trust_delta = SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()

@@

In Model 1.2, the effect of the symbols remains intact, and the effect of the weak policy condition is negative and significant (*Coef* = `r mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())-1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())+1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`]). In Model 1.3, the interaction between weak policy and real symbols is positive and significant, whereas the interaction with the fake symbols is insignificant. The interpretation of this model suggests that the real symbols had a greater effect on trust when the policy plan was weak (*Coef* = `r mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`] and `r mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`] Compared with the no symbols and fake symbols, respectively). When added to the strong policy plan, the effect of the real symbols is weaker, and significant only compared with the no symbols condition (*Coef* = `r mod_1.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1). Congruently, the symbols decreased the differences in trust between the strong and weak policies by `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())/(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())*100)%>%round(0)`%, compared with the no symbols group (from `r mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`] to `r mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`]). The interaction between symbols and information significantly contributes to the model fit (Chi2 = `r anova(mod_1.3,mod_1.2)%>%tidy()%>%filter(term=="mod_1.3")%>%select(statistic)%>%max()%>%round(2)`, *p*<.05). To facilitate the interpretation of this interaction, **Figure 6** provides a descriptive demonstration of the effects of the real symbols on trust in policy, under weak and strong information quality.

@@

The interaction between between symbols can be also tested *within-subjects*, by comparing the averaged delta across the different symbols conditions. Based on my second hypothesis, I expect that the averaged delta will be lower among subjects in the real symbols condition. This comparison is graphically displayed in **Figure 6**. The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2]%>%round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2]%>%round(2)`], *t*= `r t_delta_symbol_nosymbol[["statistic"]][["t"]]%>%round(3)` and `r t_delta_symbol_fakesymbol[["statistic"]][["t"]]%>%round(3)`, respectively). The differences between the two control groups are insignificant. These results further support my above finding that familiar symbols decrease subjects' inclination to differentiate between the strong and weak policy plans.

@@

Altogether, the above between- and within-subject analyses largely support my first two hypothesis. They suggest that familiar symbolic elements in communications increase citizens' trust in policies which are presented, and that the effect is greater the less logically persuasive is the information in the communications. Symbols attenuate the negative effect of weak or logically unpersuasive information in communications.In other statistical models, shown in the supplementary appendix, I tested additional specifications, including ##TBA##. In all these robust analyses, the effect of the real symbols condition on trust in policy remains positive and significant, and the interaction bewteen the real symbols and the weak information remains positive and signifcant [##TBA##].

How can we explain the finding that the real symbols did not increase participants' trust in the strong policy (Model 1.3)? One tentative explanation could be that symbolic elements are more effective in shifting people from low to medium levels of trust, than shifting them from medium to high levels. Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust. If this explanation holds, then result will be a cielling effect. This explantion can be also linked, theoretically, to the notion of public sector negative bias, which is well established in the Public Administration. Since most citizens tend to have implicit negative attitudes towards the public sector, they can trust public organizations up until a certain degree.[^footnote_ceilling_effect]

[^footnote_ceilling_effect]: This explanation is partly supported by a descriptive comparison of the distributions of the different groups. The comparison of the quartiles in the different groups indicates that the increase in the average was mainly due to the increase in the first quartile (i.e. the lower 25% observations). In the weak policy condition, the first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[2])%>%max()%>%round(1)` points compared with the no symbols, whereas the third quartile (i.e. the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[4])%>%max()%>%round(1)` points. In the strong policy condition, we can find similar pattern of decreasing marginal effect. The first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[2])%>%max()%>%round(1)` points, whereas the third quartile (i.e. the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[4])%>%max()%>%round(1)` points.

@@

cor_memory_nosymbol = cor.test(as.numeric(filter(SVIVA2_01_comb,SYMBOL!=1)$SYMBOL),
                               filter(SVIVA2_01_comb,SYMBOL!=1)$MEMORY_score, 
                               method="spearman")$estimate%>%mean()%>%round(2)

cor_memory_fakesymbol = cor.test(as.numeric(filter(SVIVA2_01_comb,SYMBOL!=0)$SYMBOL),
                               filter(SVIVA2_01_comb,SYMBOL!=0)$MEMORY_score, 
                               method="spearman")$estimate%>%mean()%>%round(2)
```

In **Table 2**, I test the effects of the real symbols on the elaboration measures via regression analyses. I regressed each measure on the symbols manipulation (Models 2.1, 2.3), and than added the information manipulation (Models 2.2, 2.4). The first two models, which refer to reaction time, are random intercept models which are similar to the statistical models in table 1. As for the memory score analyses, given that each subject was asked only about one policy (the second in order), I used an OLS regression.

@@

Next, I tested the hypothesis that the decrease in reaction time and memory score mediate the effect of the real symbols on trust in the weak policy plans. To do so, I used the causal mediation analysis method via `mediate` R package, which was developed by Imai et al. [@imai_2010; @imai_2011], and was also recently also implemented in Public Administration research [@porumbescu_2018]. This method predicts the change in the outcome variable (here: trust in policy) given the causal change in the mediator that would be induced by the treatment (here: decreased elaboration inducted by the real symbols). Accordingly, it enables to decipher the proportion of the causal mediation effect from the total effect. Causal mediation analysis is based on counter-factual comparisons, as opposed to the traditional method of @baron_1986, which is based on linear structural equation modeling. It is advantaged in terms of its accuracy as well as its ability to identify causality. **Table 3** displays the results of the causal mediation of reaction time (log) and memory test, under the weak policy plans.

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE}
#RT
table_med_RT__nosymbol_INFORMTION_0 = 
summary(med_RT__nosymbol_INFORMTION_0)%>%
extract_mediation_summary()

table_med_RT__fakesymbol_INFORMTION_0 = 
summary(med_RT__fakesymbol_INFORMTION_0)%>%
extract_mediation_summary()

table_med_RT__nosymbol_INFORMTION_1 = 
summary(med_RT__nosymbol_INFORMTION_1)%>%
extract_mediation_summary()

table_med_RT__fakesymbol_INFORMTION_1 = 
summary(med_RT__fakesymbol_INFORMTION_1)%>%
extract_mediation_summary()

#memory
table_med_memory__nosymbol_INFORMTION_0 = 
summary(med_memory__nosymbol_INFORMTION_0)%>%
extract_mediation_summary()

table_med_memory__fakesymbol_INFORMTION_0 = 
summary(med_memory__fakesymbol_INFORMTION_0)%>%
extract_mediation_summary()

table_med_memory__nosymbol_INFORMTION_1 = 
summary(med_memory__nosymbol_INFORMTION_1)%>%
extract_mediation_summary()

table_med_memory__fakesymbol_INFORMTION_1 = 
summary(med_memory__fakesymbol_INFORMTION_1)%>%
extract_mediation_summary()
```

@@

*Mediator: Reaction time*
```{r, echo=FALSE,warning=FALSE,message=FALSE}
table_med_RT_INFORMTION_0 = 
  cbind.data.frame(table_med_RT__nosymbol_INFORMTION_0,
                   table_med_RT__fakesymbol_INFORMTION_0)
library(kableExtra)

kable(table_med_RT_INFORMTION_0, "html",digits = 3) %>%
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
```
